COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd
fix apa tables second try
apa_table third try
corrected supplement tables
evtl. change table 1!!

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}

@@

```{r} 
apa_table(
  hypothesis1a_contrasts
)
```

@@

`r hypothesis1b_contrasts`

@@

`r hypothesis1c_mental_contrasts`

@@

`r hypothesis1c_physical_contrasts`

@@

`r hypothesis1c_time_contrasts`

@@

`r hypothesis1c_performance_contrasts`

@@

`r hypothesis1c_effort_contrasts`

@@

`r hypothesis1c_frustration_contrasts`

@@

`r hypothesis2a_contrasts`

@@

`r h2c_ss.table`

@@

<!-- (ref:Fig2cSA-caption) Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity.-->
```{r Fig2cSA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity."}

>>>>

keywords          : "effort discounting, registered report, specification curve analysis, need for cognition, n-back"
wordcount         : "X"
bibliography      : CERED.bib
floatsintext      : no
figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
csl               : nature.csl
header-includes   :
    - \usepackage{booktabs}
    - \usepackage{longtable}
    - \usepackage{array}
    - \usepackage{multirow}
    - \usepackage{wrapfig}
    - \usepackage{float}
    - \usepackage{colortbl}
    - \usepackage{pdflscape}
    - \usepackage{tabu}
    - \usepackage{threeparttable}
    - \usepackage{threeparttablex}
    - \usepackage[normalem]{ulem}
    - \usepackage{makecell}
    - \usepackage{xcolor}
    - \usepackage{setspace}\doublespacing
    - \usepackage[final]{pdfpages}

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1a_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1a XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  hypothesis1b_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1b XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
apa_table(
  hypothesis1c_mental_contrasts
  , caption = "Paired contrasts for rmANOVA hypothesis 1c mental XXX"
  , note = "XXX."
  , escape = TRUE
)
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_physical_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c physical XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_time_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c time XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_performance_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c performance XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_effort_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c effort XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis1c_frustration_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 1c frustration XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE} 
 apa_table(
   hypothesis2a_contrasts
   , caption = "Paired contrasts for rmANOVA hypothesis 2a XXX"
   , note = "XXX."
   , escape = TRUE
 )
```

@@

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  h2c_ss.table
  , caption = "Simple slope analysis of SVs...XXX"
  , note = "XXX."
  , escape = FALSE
)
```

@@

```{r Fig2cSA, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Results of the specification curve analysis for the multi level model. The upper panel shows the fixed effect estimates for Need for Cognition and n-back level as predictors of subjective values. Estimates with $p<.01$ are indicated by a dot on the line. The lower panel shows the preprocessing steps of each corresponding pipeline. The $BF10$ of each pipeline's multi level model approached infinity."}
